The Lipid Interactome Repository

### 2025-02-27 LipidProbe/1-10_FattyAcid.qmd
Berit made us new structure figures, new text in data background section
Keep finding small inconsistencies between pages
Trying to fix the dotplot framing on mobile, not much luck yet

---
title: "Trifunctional 1-10 Fatty Acid"
crossref: 
  ref-hyperlink: true # (default is true)
prefer-html: true
---

@@

:::{.border}
![](/LipidProbe/Structures/1-10_FattyAcid_Structure.png)
:::

>>>>

---
title: "Trifunctional 1-10 Fatty Acid"
prefer-html: true
---

:::{.content-hidden unless-format="html"}

:::{.border}
![Trifunctional 1-10 Fatty Acid](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
:::

@@

### 2025-02-27 StudyInformation_includes/SF_2024_B_include.qmd
Trying to fix the dotplot framing on mobile, not much luck yet

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| 1-10 FA|  min |  min  |  min |  min  |
| 8-3 FA |  min |  min  |  min |  min  |

>>>>

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| 1-10 FA|  60 min | 5 min  | 60 min | 5 min  |
| 8-3 FA |  60 min | 5 min  | 60 min | 5 min  |
